Automated Metadata Generation for Fish Specimen Image Collections

### 2021-03-29 paper/paper.tex
Small tweak in Sect. 3

Given the many thousands of images that have and will be acquired of
biological specimens, it is infeasible to generate the needed metadata
via manual, i.e. via human input, methods.  It is critical to deploy
computational techniques that will automate the process of generating
the pertinent metatdata that is essential for downstream analyses and
studies.

>>>>

Given the many thousands of images that have and will be acquired of
biological specimens, it is infeasible to generate the needed metadata
via manual, i.e. via human input, methods.  It is critical to deploy
computational techniques that will automate the process of generating
the metatdata that is essential for downstream analyses and studies.
